---
title: 'Anscombe''s Quartet: A Presentation Using ioslides'
author: "Tim Pearce"
date: "28 October 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Anscombe's  Quartet

Anscombe's Quartet consists of four pairs of vectors, with each of the x_i and y_j having:

- same mean
- same variance
- same linear correlation between each x_i and the corresponding series y_i

but different relationships between the x and y series.

## Load R prerequisites

```{r echo = FALSE}
library(datasets)
library(plotly)
attach(anscombe)
```
- Bullet 1
- Bullet 2
- Bullet 3

## Set 1

Moderately well-correlated data
```{r, echo = FALSE}
plot_ly(x = x1, y = y1, type = "scatter", mode = "markers") %>% add_lines(x = x1, y = lm(y1 ~ x1))
```

## Set 2

Quadratically-correlated data
```{r, echo = FALSE}
plot_ly(x = x2, y = y2, type = "scatter", mode = "markers") %>% add_lines(x = x2, y = lm(y2 ~ x2))
```

## Set 3

Perfectly linearly-correlated data with one outlier
```{r, echo = FALSE}
plot_ly(x = x3, y = y3, type = "scatter", mode = "markers") %>% add_lines(x = x3, y = lm(y3 ~ x3))
```

## Set 4

Independent data sets with one measurement error
```{r, echo = FALSE}
plot_ly(x = x4, y = y4, type = "scatter", mode = "markers") %>% add_lines(x = x1, y = lm(y1 ~ x1))
```

